{\bf Saint Mary Undergraduate Research Forum Committee} \hfill \textit{Univ.\ of St.\ Mary}

Assisted in development of the undergraduate research forum and moderating two panel discussions. \hfill 2022  


\vspace{\y}
{\bf Secretary, Chemistry Graduate Student Organization} \hfill \textit{Univ. of Kansas}

Served as Secretary of the inaugural administration of the Chemistry GSO. \hfill 2017-2018

\begin{itemize}[rightmargin=\dimexpr\linewidth-10cm-\leftmargin\relax,noitemsep,topsep=0cm]
\raggedright
    \item Serve as a founding member of ChemGSO, including registering ChemGSO as an official student organization.
    \item Help plan meetings with the whole Chemistry graduate student body.
    \item Take and organize minutes of meetings.
    \item Volunteer in ChemGSO organized events.
    \item Manage ChemGSO files.
\end{itemize}


\vspace{\y}
{\bf Facilitator, Jayhawks Give a Flock} \hfill \textit{Univ. of Kansas}

Served as a volunteer for University mandatory sexual assault prevention training. \hfill Sept. 2019

\begin{itemize}[rightmargin=\dimexpr\linewidth-10cm-\leftmargin\relax,noitemsep,topsep=0cm]
\raggedright
  \item Co-lead discussion with around 20 undergraduate students focused on identifying sexual assault and ways to actively prevent it.
  \item Review information provided by the KU Sexual Assault Prevention and Education Center to become familiar with active bystander sexual assault prevention.
  \item Attend training sessions for volunteers to prepare for leading discussions.
\end{itemize}
