{\bf Assistant Professor} \hfill \textit{Univ. of Saint Mary}

Physics II w/ Lab \hfill Spring 2022

Engineering Physics I w/ Lab \hfill Spring 2022

Inorganic Chemistry \hfill Spring 2022

General Chemistry I w/ Lab \hfill Fall 2021

Physics I w/ Lab \hfill Fall 2021

Science of Cooking w/ Lab \hfill Fall 2021

\vspace{6pt}
Research Mentoring
\begin{itemize}[rightmargin=0pt]
  \item Gabrielle Moore: Determination of Copper in Water \hfill Spring 2022\linebreak Using PEI and UV-Vis Spectroscopy
  \item Rebecca Porter: Weather Patterns Surrounding Wind Chill \hfill Spring 2022\linebreak Extremes in Georgia
\end{itemize}
\vspace{\y}

{\bf Graduate Teaching Assistant} \hfill \textit{Univ.\ of Kansas}

\hfill \textit{Dept.\ of Chemistry}

Physical chemistry for engineers lecture TA: \hfill Fall 2020
\begin{itemize}[rightmargin=\dimexpr\linewidth-10cm-\leftmargin\relax,noitemsep,topsep=0cm]
\raggedright
  \item Lead weekly virtual discussion sessions to practice problem solving and review concepts. Zoom breakout sessions allowed for smaller groups which I could check in with separately.
  \item Hold regular office hours. Help students learn general problem solving approaches and discuss concepts.
  \item Write detailed solutions and grade weekly problem sets and computational exercises.
  \item Grade exams.
\end{itemize}

\vspace{\y}
Physical chemistry laboratory instruction including: \hfill Spring 2020
\begin{itemize}[rightmargin=\dimexpr\linewidth-10cm-\leftmargin\relax,noitemsep,topsep=0cm]
\raggedright
  \item Shift lab sessions to online format during campus shutdown due to COVID-19
  \item Lead pre-lab discussions focused on connecting the procedure to the underlying concepts.
  \item Oversee lab procedures and troubleshoot wet lab and computational
  exercises.
  \item Hold office hours. Provide guidance and lead students towards solving problems independently.
  \item Grade informal and formal lab reports, including design of my own rubric
\end{itemize}

\vspace{\y}
Organic chemistry laboratory instruction including: \hfill Fall 2016
\begin{itemize}[rightmargin=\dimexpr\linewidth-10cm-\leftmargin\relax,noitemsep,topsep=0cm]
\raggedright
  \item Lead pre-lab discussions
  \item Provide safety lessons and ensure compliance with safety procedures
  \item Grade lab reports and tests
  \item Hold office hours to facilitate student problem solving and writing
\end{itemize}


\vspace{\y}
{\bf Undergraduate research mentor} \hfill \textit{Univ. of Kansas}

\hfill Fall 2019 - Spring 2021

\begin{itemize}[rightmargin=\dimexpr\linewidth-10cm-\leftmargin\relax,noitemsep,topsep=0cm]
\raggedright
  \item Provide context and guidance for approaching computational research.
  \item Introduce programming skills necessary for computational research.
  \item Assess understanding of the research question, and problem solve alongside the student to improve weak spots.
\end{itemize}
